Proposed Solution

### 2016-01-29 system.tex
random

\section{Quantum Types}

@@

foo = 300
bar = 300.txt

@@

This idea is closely related to exstentially quantified types.

>>>>

\section{Learning the Rules}
\label{sec:system}

Before describe how our system for learning rules is working, we first outline a translator which converts configuration files into an intermediary representation. Typing is based on already given set of basic types. However, typing is also a system module than can be easily extended to support
more types. In that case the user will need to provide rules for type inference and probability

\subsection{From Untyped Expressions to Quantum Types}

Typing the untyped expressions appearing in configuration files 
is the first step in parsing and translating the data. 
Configuration files usually consist of variable assignments, or some simple instructions about including files or libraries. We initially
collect all assignments into a set of pairs $(n, v)$, where $n$ denotes 
variable name and $v$ denotes variable value. However, based only on the 
value $v$ we cannot determine the type of $n$.

Consider for instance the following example:\\
\texttt{\hspace*{2em}foo = 300\\
\hspace*{2em}bar = 300.txt}\\
Most likely \texttt{foo} is an integer, but it could also be a string.
In the latter case we want to learn the rule $ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. We introduce {\emph{quantum types}} to 
address this issue.

Let $\mathcal{T}$ be a set of basic types. In \app set $\mathcal{T}$ contains strings, integers, file paths, sizes and IP addresses. 
A quantum type built from $\mathcal{T}$ is a list of pairs $[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$ such that $\tau_i \in \mathcal{T}$ 
and $\Sigma p_i = 1$.

@@

@@

This idea is closely related to existentially quantified types.
